---
title: "word-freq"
author: "Andrew"
date: "02/10/2022"
output: rmarkdown::github_document
        #toc: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidytext)
library(readtext)
library(dplyr)
library(ggplot2)
library(wordcloud)
library(kableExtra)
#devtools::install_github("ChristopherLucas/translateR")
library(translateR)
library(stringr)
```

# Frequency of words in a book
## Data prep

### Load the text file and tokenise words: 
```{r}
book_pt <- readtext(file = "hp-01.txt", encoding = "utf-8")
summary(book_pt)
```

```{r}
book_pt_token <- book_pt %>%
        unnest_tokens(word, text)
```

### Add portuguese stop words:
```{r}
# source: https://gist.github.com/alopes/5358189
stop_pt <- c('de', 'a', 'o', 'que', 'e', 'do', 'da', 'em', 'um', 'para', 'é', 'com', 'não', 'uma', 'os', 'no', 'se', 'na', 'por', 'mais', 'as', 'dos', 'como', 'mas', 'foi', 'ao', 'ele', 'das', 'tem', 'à', 'seu', 'sua', 'ou', 'ser', 'quando', 'muito', 'há', 'nos', 'já', 'está', 'eu', 'também', 'só', 'pelo', 'pela', 'até', 'isso', 'ela', 'entre', 'era', 'depois', 'sem', 'mesmo', 'aos', 'ter', 'seus', 'quem', 'nas', 'me', 'esse', 'eles', 'estão', 'você', 'tinha', 'foram', 'essa', 'num', 'nem', 'suas', 'meu', 'às', 'minha', 'têm', 'numa', 'pelos', 'elas', 'havia', 'seja', 'qual', 'será', 'nós', 'tenho', 'lhe', 'deles', 'essas', 'esses', 'pelas', 'este', 'fosse', 'dele', 'tu', 'te', 'vocês', 'vos', 'lhes', 'meus', 'minhas', 'teu', 'tua', 'teus', 'tuas', 'nosso', 'nossa', 'nossos', 'nossas', 'dela', 'delas', 'esta', 'estes', 'estas', 'aquele', 'aquela', 'aqueles', 'aquelas', 'isto', 'aquilo', 'estou', 'está', 'estamos', 'estão', 'estive', 'esteve', 'estivemos', 'estiveram', 'estava', 'estávamos', 'estavam', 'estivera', 'estivéramos', 'esteja', 'estejamos', 'estejam', 'estivesse', 'estivéssemos', 'estivessem', 'estiver', 'estivermos', 'estiverem', 'hei', 'há', 'havemos', 'hão', 'houve', 'houvemos', 'houveram', 'houvera', 'houvéramos', 'haja', 'hajamos', 'hajam', 'houvesse', 'houvéssemos', 'houvessem', 'houver', 'houvermos', 'houverem', 'houverei', 'houverá', 'houveremos', 'houverão', 'houveria', 'houveríamos', 'houveriam', 'sou', 'somos', 'são', 'era', 'éramos', 'eram', 'fui', 'foi', 'fomos', 'foram', 'fora', 'fôramos', 'seja', 'sejamos', 'sejam', 'fosse', 'fôssemos', 'fossem', 'for', 'formos', 'forem', 'serei', 'será', 'seremos', 'serão', 'seria', 'seríamos', 'seriam', 'tenho', 'tem', 'temos', 'tém', 'tinha', 'tínhamos', 'tinham', 'tive', 'teve', 'tivemos', 'tiveram', 'tivera', 'tivéramos', 'tenha', 'tenhamos', 'tenham', 'tivesse', 'tivéssemos', 'tivessem', 'tiver', 'tivermos', 'tiverem', 'terei', 'terá', 'teremos', 'terão', 'teria', 'teríamos', 'teriam')
stop_pt <- as_tibble(stop_pt)
```

### Add character names as stop words (more to add):
```{r}
char_names <- c("harry", "potter", "dursley", "rony", "hermione", "hagrid", "snape", "dumbledore") %>% as_tibble()
```

## Visualisations
Top 20 words and their frequency:
```{r}
book_pt_token_subset <- book_pt_token %>% 
        count(word, sort = TRUE) %>%
        anti_join(stop_pt, by = c("word" = "value")) %>%
        anti_join(char_names, by = c("word" = "value"))

book_pt_token_subset %>% 
        top_n(20, wt = n) %>%
        ggplot(aes(x = reorder(word, n), n)) +
        geom_bar(stat = "identity") +
        coord_flip() +
        xlab("Palavra") +
        ylab("Frequência") +
        theme_bw()
```

### Generate a word cloud with the top 100 words:
```{r}
wordcloud(
        words = book_pt_token_subset$word,
        freq = book_pt_token_subset$n,
        min.freq = 1,
        max.words = 100,
        random.order = FALSE,
        colors = brewer.pal(7, "Greens")
)
```

### Top 1000 words:
<details>
  <summary>Full list: </summary>
TODO: Add a translation col 
```{r}

book_pt_token_subset %>% 
        top_n(1000, wt = n) %>% 
  kable(format = "pipe", col.names = c('Word', 'Frequency'))

# google.dataset.out <- translate(dataset = book_pt_token_subset,
#                                 content.field = 'word',
#                                 google.api.key = #,
#                                 source.lang = 'en',
#                                 target.lang = 'pt')
```  
</details>


## Sentence mining
In progress. Loop through a subset of most common words and extract the first matching sentence for each word. 
```{r}
# book_pt_token_subset_10 <- book_pt_token_subset %>% 
#         top_n(10, wt = n)
# 
# book_pt_sentences <- tibble(text = book_pt) %>% 
#   unnest_tokens(sentence, text, token = "sentences")
```

```{r}
# asdf <- book_pt_sentences[str_detect(book_pt_sentences$sentence, "dumbledore"), ]
# asdf[[1,1]]
```


